PineAPPL:\\ EW and mixed QCD--EW corrections for PDF fits

### 2020-08-01 paper/sec-results.tex
more on Sect.3

In comparison to the PDF uncertainty, the size of the EW correction is
always larger, especially at the boundaries of the distribution. This fact
suggests that, once included in a global fit, EW corrections could recast the
relative weight of each data set included in the fit, and possibly lead to
an improvement in their overall description. In comparison to the scale
uncertainty, the size of the EW correction is similar, except for the four bins
at the largest invariant mass, where the latter is significantly larger than
the former. The size of the scale variation is the same for the QCD and the
QCD+EW theories. These facts suggest that the NNLO QCD correction is comparable
to the NLO QCD+EW correction, except at very large values of the invariant mass,
where the EW correction still dominates. This result stresses the need to
include the EW corrections in order to obtain an accurate description of the
large invariant mass bins. Finally, the Monte Carlo statistical
uncertainty remains negligible in comparison to the data, PDF and scale
uncertainties, and to the size of the EW correction. Our conclusions are
therefore not affected by a poor simultaion of the underlying events.

@@

In general, the size of the EW corrections is

@@

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TPT}%
    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TTM}
    \caption{PineAPPL comparison for ATLAS top pair.}
    \label{fig:atlastop}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMS_Z_13_TEV}
    \caption{PineAPPL comparison for CMS $Z$ $p_T$ distribution.}
    \label{fig:cmsZ13TeV}
\end{figure}

>>>>

In comparison to the PDF uncertainty, the size of the EW correction is
always larger, especially at the boundaries of the distribution. This fact
suggests that, once included in a global fit, EW corrections could recast the
relative weight of each data set included in the fit, and possibly lead to
an improvement in their overall description. In comparison to the scale
uncertainty, the size of the EW correction is similar, except for the four bins
at the largest invariant mass, where the latter is significantly larger than
the former. The size of the scale variation is the same for the QCD and the
QCD+EW theories. These facts suggest that the NNLO QCD correction is comparable
to the NLO QCD+EW correction, except at very large values of the invariant mass,
where the EW correction still dominates. This result stresses the need to
include the EW corrections in order to obtain an accurate description of the
large invariant mass bins. Finally, the Monte Carlo statistical
uncertainty remains negligible in comparison to the data, PDF and scale
uncertainties, and to the size of the EW correction. Our conclusions are
therefore not affected by a poor simulation of the underlying events.

@@

In general, the size of the EW corrections is comparable to or slightly larger
than the data uncertainty, except for the invariant mass bin 
45~GeV$<M_{\ell\bar\ell}<$60~GeV, where the shift due to the EW correction
overshoots the data uncertainty by about a factor of ten, and at large
rapidities, where the shift due to the EW correction, although it can become
large, is always a fraction of the data uncertainty. As already observed in the
case of the ATLAS measurement, should EW corrections be included in a fit of
PDFs, the description of the precise bins in the low invariant mass range is
likely to benefit from the more accurate theory and the kinematic cut that
excludes any data point at large invariant mass and/or rapidity can be safely
removed.

In comparison to the PDF uncertainty, the size of the EW corrections is always
larger. We therefore anticipate that, once included in a PDF fit, they would
recast the relative weight of each data set included in the fit, and possibly
lead to an improvement in their overall description. In comparison to the scale
uncertainty, the size of the EW correction is similar, except on the $Z$-boson
mass peak, 60~GeV$<M_{\ell\bar\ell}<$120~GeV, where the scale uncertainty exceeds
the size of the EW correction by about a factor of five. These facts confirm,
as expected, that EW corrections are almost immaterial at the $Z$-boson mass
peak, but that NNLO QCD corrections are otherwise as relevant as NLO QCD+EW
corrections. Finally, the Monte Carlo statistical uncertainty remains negligible
in comparison to the data, PDF and scale uncertainties, and to the size of the
EW correction, except for a couple of bins at forward rapidity in the highest
invariant mass bins. Improving the Monte Carlo statistical precision will
require to generate an unrealistically large number of events; therefore, it
might be desirable to treat this uncertainty as an additional theoretical
uncertainty in the PDF fit~\cite{Ball:2018lag}.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TPT}%
    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TTM}
    \caption{Same as Fig.~\ref{fig:atlaszhighmass49fb}, but for the ATLAS
      differential top-quark pair measuremen at a centre-of-mass energy of
      8~TeV~\cite{Aad:2015mbv}. Displayed are the distributions in the
      transverse momentum of the top quark $p_T^t$ (left), and in the invariant
      mass of the top-quark pair $m_{t\bar{t}}$ (right).}
    \label{fig:atlastop}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMS_Z_13_TEV}
    \caption{PineAPPL comparison for CMS $Z$ $p_T$ distribution.}
    \label{fig:cmsZ13TeV}
\end{figure}
